---
title: "Interactive results"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    theme: paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	include = FALSE
)
library(readr)
library(dplyr)
library(ggplot2)
library(plotly)
library(crosstalk)
library(flexdashboard)
library(purrr)
library(tidyr)
library(here)
```

```{r read_data}
all.results <- read_csv(
	here(
		"DATA",
		"expose_2_prescr_PD-4prescr-levo-mao-b_age-time-scale_results_atc2level_all.csv"
		)
	)
```

> **RESULTS from Cox-regression analysis:**

> - exposure defined as min.2 prescriptions;
> - age as the time scale;
> - PD defined as 4 prescriptions of levodopa (+ reimbursement codes) **OR** mao-b inhibitors (N04BD);
> - adjusted p-values calculated with the Benjamini & Yakutieli method to control for false discovery rate.


Column {.tabset}
-----------------------------------------------------------------------

### Sorted by ATC code

```{r sort_by_atc}
cur.results <- all.results
```


```{r plot_ggplotly, eval=TRUE, include=TRUE, echo=FALSE, warning=FALSE, out.height='100%'}
# create two columns: one for selection, the other for plot
shared.atc <- SharedData$new(cur.results)
 
plot.sort.atc <-
	ggplot(shared.atc, aes(HR, ATC_code, text = hover.text)) +
	geom_point(aes(color = as.factor(group))) +
  geom_errorbarh(aes(xmin = HR_l, xmax = HR_u, color = as.factor(group))) +
  geom_vline(aes(xintercept = 1), color = "grey") +
	scale_x_continuous(name = "HR", trans = "log") +
  coord_cartesian(xlim = c(NA, 10)) +
  theme_minimal() +
  theme(legend.position = "none") +
  xlab("HR") + ylab("ATC code")

bscols(widths = c(3, NA),
	list(
		filter_checkbox(id = "p-val_exclude", label = "P-value filtering",
				sharedData = shared.atc, group = ~p.val.group, inline = TRUE),
		filter_slider(id = "x_range", label = "HR filtering",
				sharedData = shared.atc, column = ~HR, round = 1),
		filter_checkbox(id = "users_range", label = "no. of users per drug",
				sharedData = shared.atc, group = ~users.group, inline = TRUE),
		filter_checkbox(id = "atc_series", label = "ATC series filtering",
				sharedData = shared.atc, group = ~group)
	),
	ggplotly(plot.sort.atc, height = nrow(cur.results) * 10,
						tooltip = c("y", "text"))
)

```

### Sorted by HR value

```{r sort_by_pv}
cur.results <- all.results
hr.order <- order(cur.results$HR)
cur.results$ATC_code <- factor(cur.results$ATC_code,
		levels = cur.results$ATC_code[ hr.order ], ordered = TRUE)
```

```{r plot_ggplotly,include=TRUE,echo=FALSE,warning=FALSE, out.height='100%'}
```

### Sorted by p-value

```{r sort_by_hr}
cur.results <- all.results
pv.order <- order(cur.results$p.adj.FDR, decreasing = TRUE)
cur.results$ATC_code <- factor(cur.results$ATC_code,
		levels = cur.results$ATC_code[ pv.order ], ordered = TRUE)
```

```{r plot_ggplotly,include=TRUE,echo=FALSE,warning=FALSE, out.height='100%'}
```


### Table view


```{r table,include=TRUE,echo=FALSE,out.height=1200, fig.height=100}
DT::datatable(
	all.results %>%
		select(ATC_code, name, HR, HR_l, HR_u, pvals, p.adj.FDR, N.nonpd, N.pd) %>%
		mutate(across(HR:p.adj.FDR, ~ signif(.x, digits = 2))) %>% 
		tidyr::unite("HR_CI", HR_l:HR_u, sep = "-"),
	class = "compact",
	colnames = c("ATC code", "drug name", "hazard ratio (HR)", "95% CI", "p-value",
							 "p-value (FDR-adj.)", "# users without PD", "# users with PD"),
	fillContainer = TRUE,
	height = 2000,
	width = '80%',
	rownames = FALSE,
	extensions = c('FixedHeader', 'Buttons'),
	options = list(
		scrollCollapse = FALSE,
		fixedHeader = TRUE,
		lengthMenu = c(50, 100, 200, 500, -1),
		dom = 'Bfrtip',
		buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
	)
)
```


